Measurement Clusterization in Bayesian D-optimal Designs in Infinite Dimensions

### 2024-08-25 latex/ba.tex
answered refs
Now with abstract

  In this study, we consider Bayesian D-optimal designs, i.e.~designs
  that maximize the expected Kullback-Leibler divergence between
  posterior and prior. We propose an analytically tractable model for
  D-optimal designs over Hilbert spaces. In this framework, we make
  several key contributions: \textbf{(a)} We establish that
  measurement clusterization is a generic trait of D-optimal designs
  with independent Gaussian measurement errors, and prove that
  introducing correlations among measurement error terms mitigates
  clusterization. \textbf{(b)} We characterize D-optimal designs as
  reducing uncertainty across a subset of prior covariance
  eigenvectors. Finally, \textbf{(c)} We leverage this
  characterization to argue that measurement clusterization arises as
  a consequence of the pigeonhole principle: when more measurements
  are taken than there are locations where the select eigenvectors are
  large and others are small --- clusterization occurs.
\end{abstract}

@@

\bibliographystyle{ba}
\bibliography{/Users/yairdaon/work//lib.bib}

>>>>

  In this study, we consider Bayesian D-optimal designs, i.e.~designs
  that maximize the expected Kullback-Leibler divergence between
  posterior and prior. We propose an analytically tractable model for
  D-optimal designs over Hilbert spaces. In this framework, we make
  several key contributions: \textbf{(a)} We establish that
  measurement clusterization is a generic trait of D-optimal designs
  for linear inverse problems with independent Gaussian measurement
  errors and a Gaussian prior. \textbf{(b)} We prove that introducing
  correlations among measurement error terms mitigates
  clusterization. \textbf{(c)} We characterize D-optimal designs as
  reducing uncertainty across a subset of prior covariance
  eigenvectors. \textbf{(d)} We leverage this characterization to
  argue that measurement clusterization arises as a consequence of the
  pigeonhole principle: when more measurements are taken than there
  are locations where the select eigenvectors are large and others are
  small --- clusterization occurs. Finally, we use our analysis to
  argue against the use of Gaussian priors with linearized physical
  models when seeking a D-optimal design.
\end{abstract}

@@

\bibliographystyle{ba}
\bibliography{/Users/yairdaon/work/lib.bib}
